Analysis and Figures for Gallego et al, 2020

### 2020-09-05 Manuscript/What.lies.ahead.reviewed.tex
Wilcox results done

Given such heterogeneity in projections, gains and losses tend to balance one another out when looking at richness variation within phyla; {\color{red} we find no change in median richness for the year 2095 relative to the present in the Hood Canal (taxon richness by year, Wilcoxon p $=$ 0.7). Diatoms, however, show consistent and significant declines in richness in that region (Wilcoxon p $< 10^{-16}$). } {\color{blue} RAMON - can you clarify here? there should be comparisons for A. 2017 vs 2095 in overall richness, for both HC and SJI.  Then B. same for Diatom richness, dinoflagellate richness, or anything else you find interesting.}

>>>>

Given such heterogeneity in projections, gains and losses tend to balance one another out when looking at overall richness variation; {\color{red} we find no change in median richness for the year 2095 relative to the present in the Hood Canal (taxon richness by year, Wilcoxon p $=$ 0.7); while higher diversity is expected in the San Juan Island in 2095 (increase in median species richness of 2.1, Wilcoxon p $=$ 0). Diatoms, however, show consistent and significant declines in richness in the Hood Canal (Wilcoxon p $< 10^{-16}$), while the changes on the San Juan Island are undetectable (p $=$ 0.8).  Dinoflagellates see their richness increase in both regions with the future scenario(Wilcoxon p $< 10^{-50}$) }.{\color{blue} RAMON - can you clarify here? there should be comparisons for A. 2017 vs 2095 in overall richness, for both HC and SJI.  Then B. same for Diatom richness, dinoflagellate richness, or anything else you find interesting.RYAN - See what you think}

### 2020-09-05 Scripts/Manuscript.Main.Analysis.Rmd
Wilcox results done

expanded.future <- future.scenario %>% 
  select(Area, Year, Temperature = Temp.std, TemperatureCelsius, pH = pH.std, pH_units) 
nsims <- nrow(future.scenario)
## Get

@@

#overall change in richness
richness.by.point %>%
  group_by(Year, Area) %>%
  summarise(median(richness))
#diatom change in richness
richness.by.phylum.by.point %>%
  filter(phylum == "Bacillariophyta") %>%
  group_by(Year, Area) %>%
  summarise(median(richness))
```

@@

richness.by.phylum.by.point %>% 
   nest(-phylum,-Area) %>% 
   mutate(wilcoxon = map (data, ~ wilcox.test(richness ~ Year, data = .x) ),
          wiloc.tidy= map_df(wilcoxon, broom::tidy))  -> results.lm

results.lm %>%  filter (phylum == "Bacillariophyta")
```

>>>>

expanded.future <- future.scenario %>% 
  select(Area, Year, Temperature = Temp.std, TemperatureCelsius, pH = pH.std, pH_units)

## Get

@@

#overall change in richness
richness.by.point %>%
  group_by(Year, Area) %>%
  summarise(median(richness))
#diatom change in richness
richness.by.phylum.by.point %>%
  filter(phylum == "Bacillariophyta") %>%
  group_by(Year, Area) %>%
  summarise(median(richness))
richness.by.phylum.by.point %>%
  filter(phylum == "Dinophyceae") %>%
  group_by(Year, Area) %>%
  summarise(median(richness))
```

@@

richness.by.phylum.by.point %>% 
   nest(-phylum,-Area) %>% 
   mutate(wilcoxon = map (data, ~ wilcox.test(richness ~ Year, data = .x) ),
          wiloc.tidy= map(wilcoxon, broom::tidy))  -> results.lm

results.lm %>%  filter (phylum == "Bacillariophyta") %>% unnest(wiloc.tidy)

results.lm %>%  filter (phylum == "Dinophyceae") %>% unnest(wiloc.tidy)

results.lm %>% 
  unnest(wiloc.tidy) %>%

  ggplot(aes(x = phylum , y = `p.value`)) +
  geom_point(aes(color = Area))
```
